### 2013-07-30 summary.tex
Hell Week Monday 11AM update.
where are my cannolis
8 hours qq

The non-technical summary is like an abstract, but without any technical
terminology. So instead of $v = (v_0, v_1, \ldots, v_n)$, you might say
something along the lines of ``pick a point in high-dimensional space.''
Don't worry about this section yet; you'll receive more guidance
later on, when you're near the end of your mentorship.

>>>>

We take a certain class of maps and represent them with colored diagrams.  These colored diagrams provide a combinatorial way for us to study and compute these maps.  Now an algorithm of Libedinsky allows us to construct such diagrams from a string of $1$'s and $0$'s; furthermore, we can ocmpose two such diagrams together to obtain a third diagram.   We develop tools to compute this third diagram based on the original binary strings.

%TODO write one
